Supernova Host Galaxies in the Dark Energy Survey: \\ II. Rapidly Evolving Transients

### 2020-02-17 RET_Hosts.tex

>>>>

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/mag_dist.png}
\caption{Observer-frame $r$-band magnitude distribution for the host galaxies of RETs in DES. The orange histogram represents the 97/106 DES RETs for which a host was detected. The green histogram shows those that did not have a successful redshift measurement, while blue shows those with no redshift despite being targetted by OzDES.
\label{fig:sfms_sfr}}
\end{figure}
